Catchy Title Goes Here

### 2018-05-02 Paper/paper.tex
updated paper, added figures

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Although we have chosen a flexible functional form to represent the force of infection and vaccination hazards, we know that that the true functions present in nature are unlikely to be precisely matched by Weibull distributions. This will necessarily lead to some level of biases in our inferences. To understand these possible biases, we analyze simulated data with known foi, vh, and $\gamma$ (vaccine efficacy), and examine the results.  
Results:
Simulation experiment ? illustrate for 10 levels of vaccine effectiveness:
	a) Does fitted model using vaccination and case data only recover the true seroprevalence?
	b) Need to show that it recovers the vaccination hazard as well
	c) show estimate of vaccine effectiveness
Figure 1 ? 3-panel figure illustrating those 3 points

>>>>

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Although we have chosen a flexible functional form to represent the force of infection and vaccination hazards, we know that that the true functions present in nature are unlikely to be precisely matched by Weibull distributions. This will necessarily lead to some level of biases in our inferences. To understand these possible biases, we analyze simulated data with known foi, vh, and $\gamma$ (vaccine efficacy), and examine the results.

Figure~\ref{fig:foivhsimdata} shows the injected (dashed lines) and recovered (solid (purple or orange) lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy of $\gamma = 0.9$ (orange) and $\gamma = 0.6$ (indigo). The top panel shows the force of infection, and it is very clear from this panel that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in Figure~\ref{fig:veffsimdata}.

\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/foivhaz_fakedata_vaxserocase.pdf}
\caption{caption\label{fig:foivhsimdata}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/veff_fakedata.pdf}
\caption{caption\label{fig:veffsimdata}}
\end{figure}

This Figure shows the posterior distributions and injected values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the injected values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth nothing that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

The bottom panel in this same Figure shows the inferred values for vaccine efficacy using only case and vaccination data - i.e. leaving out the serology data from the analysis. For the higher levels of $\gamma$, the results are dominated by the prior. For the lower values, we are again biased quite low, but also again recover the correct ranking of vaccine efficacy.

Finally, we wish to explore the recovered fits to the true data when analyzing only the case and vaccination data. These results are shown in Fig.~\ref{fig:svcsimdata}. Here, we show the recovered (lines) vaccination prevalence, seroprevalence, and case distribution for simulated data with vaccine efficacy of $\gamma = 0.6$ (indigo) and $\gamma = 0.9$ (orange). The true values for each of these are shown as points. We can see that the case and vaccination data are fit well by the recovered model parameters - unsurprising, given that this is the data that was used in the fitting analysis. The seroprevalence data is also fit well in the case of $\gamma = 0.9$, which recall is one of the values for which the posterior on $\gamma$ is essentially the same as the prior, which includes a lot of weight at the true value. The seroprevalence when $\gamma = 0.6$ is much more biased, although it still follows some of the qualitative features of the true data. Thus for values of vaccine efficacy that are near to the peak of our prior distribution, the seroprevalence inferred using only vaccination and case data is quite accurate. For lower vaccine efficacies, though, seroprevalence data is almost certainly needed to achieve an accurate picture.

\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/vsc_simdata_vaxcase.pdf}
\caption{caption\label{fig:svcsimdata}}
\end{figure}
